Supplementary Information: Tropical tree drought sensitivity is jointly shaped by drought characteristics, species adaptations, and individual microenvironments

### 2025-06-25 doc/manuscript_hkk_drought_sensitivity.Rmd
updated manuscript with table

```{r table, eval=F, echo=FALSE, warning=FALSE, message=FALSE}
# figure 0-----------------------------

@@

# Table Caption {-}

**Table 1. Summary table of hypotheses tested, effects of variables on drought sensitivity and corresponding evidence.** For each variable x year combination, "+" indicates a positive effect, "-" indicates a negative effect and "n.s." indicates that the effect was not statistically significant.

>>>>

@@

# Tables {-}

```{r table, echo=FALSE, warning=FALSE, message=FALSE}
# figure 0-----------------------------
